???A quantitative framework for investigating the reliability of network construction

### 2017-11-20 manuscript/CI_interactions.tex
fixed a compilation error

    Now, consider the case where the two species have never been observed interacting across $n$ trials, i-e. $k=0$. The question is then ``what is the probability these two species do not interact''$? Since it is not possible to prove that the two species could never interact (strickly speaking, in such an approach $\lambda=0$ is impossible), given the framework above we must fix a threshold below which we consider that there is no interaction ($\lambda~0$). We call this threshold probability $\lambda*$. We then use the cumulative distribution function to estimate $P(\lambda<\lambda*|L=0,n)$ for different $n$. The 
    function plot\_precision in \emph{Appendix S2} calculates distribution function for $\lambda*$ with an increasing number of trials. The figure below illustrates this distribution for $\lambda*$=0.1. This yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than 0.1 (recall Fig.~\ref{upper_limits}). Note the special case where there is no observation of the two species co-occurring, $n = 0$  In this situation, the posterior distribution converges to the prior distribution since the data include no information on the probability with which species might interact should they co-occur; see above).

@@

      Importantly, while large, this network illustrates the very real constraints on the sampling of ecological networks. As a baseline, we may compare the frequency of co-occurrence of taxa to reveal the challenge of having sufficiently large $n_{ij}$ (Fig.~\citep{upper_limits}). In the example data, most (3986 out of 4992) pairs of species are never found co-occurring, and for species found co-occurring the number of co-occurrences was generally low (Fig.~\ref{histograms}A). 
%DG: can you provide mean and variance in the text?
      Among the species which did sometimes interact when co-occurring, the incidence of interaction was actually low. 
%DG: in the following, would be useful to present both absolute and relative numbers, or just relative
      Only 141 pairs of species were observed interacting: of these, 26 were observed interacting only once and 48.2\% were observed interacting five or fewer times (Fig.~\ref{histograms}B). Thus, even in the most extensive data set that we could find, limited sampling is clearly a major source of uncertainty.

>>>>

    Now, consider the case where the two species have never been observed interacting across $n$ trials, i-e. $k=0$. The question is then ``what is the probability these two species do not interact''? Since it is not possible to prove that the two species could never interact (strickly speaking, in such an approach $\lambda=0$ is impossible), given the framework above we must fix a threshold below which we consider that there is no interaction ($\lambda \sim 0$). We call this threshold probability $\lambda*$. We then use the cumulative distribution function to estimate $P(\lambda<\lambda*|L=0,n)$ for different $n$. The 
    function plot\_precision in \emph{Appendix S2} calculates distribution function for $\lambda*$ with an increasing number of trials. The figure below illustrates this distribution for $\lambda*$=0.1. This yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than 0.1 (recall Fig.~\ref{upper_limits}). Note the special case where there is no observation of the two species co-occurring, $n = 0$  In this situation, the posterior distribution converges to the prior distribution since the data include no information on the probability with which species might interact should they co-occur; see above).

@@

      Importantly, while large, this network illustrates the very real constraints on the sampling of ecological networks. As a baseline, we may compare the frequency of co-occurrence of taxa to reveal the challenge of having sufficiently large $n_{ij}$ (Fig.~\ref{upper_limits}). In the example data, most (3986 out of 4992) pairs of species are never found co-occurring, and for species found co-occurring the number of co-occurrences was generally low (Fig.~\ref{histograms}A). 
%DG: can you provide mean and variance in the text?
      Among the species which did sometimes interact when co-occurring, the incidence of interaction was actually low. 
%DG: in the following, would be useful to present both absolute and relative numbers, or just relative
      Only 141 pairs of species were observed interacting: of these, 26 were observed interacting only once and 48.2\% were observed interacting five or fewer times (Fig.~\ref{histograms}B). Thus, even in the most extensive data set that we could find, limited sampling is clearly a major source of uncertainty.
